PDBF Documentation

### 2015-05-18 Documentation.tex
!

@@

\noindent Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\
Note: if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay\\[8pt]
\noindent Options:\\[3pt]
%
Common options\\[4pt]
%
\option
{width}
{Sets the width of the chart.}
{\LaTeX\relax length}
{No default value. Value must always be set!}

>>>>

\section{SQL queries}
attributes with spaces sourrounded by square bracets. E.g. SELECT a AS [This is a test] FROM test;\\
TODO: write about special sql functions. link to alasql.\\
\verb|GRUBBS_FILTER(arr, alpha)|: \\
\verb|MEAN(arr)|: \\
\verb|STDDEV_SAMP(arr)|: \\
\verb|MARGIN_OF_ERROR(arr, alpha)|: \\
\verb|CONF_INT(arr)|: \\
\verb|T_TEST(arr1, arr2, alpha)|: \\
\verb|WELCH_TEST(arr1, arr2, alpha)|: \\

@@

\noindent Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\
Note: if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay.\\
Note: The first column of the query result is used for the x-Axis, all other columns are used for y-Axis.\\[8pt] 
\noindent Options:\\[3pt]
%
Common options\\[4pt]
%
\option
{width}
{Sets the width of the chart.}
{\LaTeX\relax length}
{No default value. Value must always be set!}
